\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Implementation of a Flow-sensitive Pointer Analysis}
\author{Shiry Hassan  200175016}
\date{August 2017}

\begin{document}

\maketitle

\section{Introduction} I choose to implement a flow sensitive pointer analysis.

\section{Implementation} I implemented a new package called pa.\\
Pa contains classes as PaDomain, PaState, PaMain, PaFactoid and more classes for the transformers.

\subsection{PaFactoid} The object represent a points-to-vertex.\\
The edge can be represented with a label or without.\\
So I support both when x = y or for example x.f = y (when there is no field, it is initialized to null).

\subsection{PaDomain}
$[x = null] \ \ \ Remove \ (x) \bigcup \ (x = null)$\\
$[x.f = null]\ \ \ Remove \ (x) \bigcup \ $(find x.f factoid and update $x.f= null)$\\
$[x = y]\ \ \ Remove \ (x) \bigcup \ (x = y)$\\
$[x = y.f]\ \ \ Remove \ (x) \bigcup \ $ find y.f factoid and $x = y.f null)$\\
$[x = new T]\ \ \ Remove \ (x) \bigcup \ (x =  new T)$
$[x.f = y]\ \ \ Remove \ (x) \bigcup \ $(find x.f factoid and update $x.f= y)$\\\\
leq(PaState first, PaState second)\\
Returns true if second states contains all first states and false otherwise.\\\\
ub(PaState first, PaState second)\\
Returns the join of the two states (weak update). 



\subsection{PaState}
Inherits parents methods.\\
(Tried to override toString() but unsuccessfully)

\subsection{PaMain} In a similar way to the cp main.

\section{Testing}
	public int checkLocalToLocal(Integer a, Integer b, Integer c)\\
	
    a = new Integer(1);     a = labelnew0\\
        
		b = new Integer(2);        b = labelnew1\\
		
		$if(a == c)$\\
		
			
			$c = a;$                    // c points to     labelnew0\\
		
		    $if(b == c)$\\
		
		
			$c = b;	   $         // c points to labelnew1\\
			
		return c;

\section{Conclusion}
 The analysis is precise when it is a Strong update.\\ When it's sure which one to exchange with the updated state it is  must-point-to query.\\ We can see it along the transformers except for x.f = y when x can has other fields so it is a weak update.\\ It's a may alias query when there are some more than one field for x and join the those states.
 
 
 \section*{Questionnaire (optional)}
Please provide feedback for this assignment:
\begin{enumerate}
\item \textbf{Q:} Was this assignment useful for understanding the material?

      \textbf{A:} Yes sure, it makes more sense when you implement it.\\ Also I got to practise java and computing. 

\item \textbf{Q:} How much time did you spend on this assignment?

      \textbf{A:} About 50 hours.

\item \textbf{Q:} How hard would you say this assignment was: trivial/easy/okay/hard/very challenging?

      \textbf{A:} I think it was okay it wasn't easy but not too hard.\\ It took sometime to understand what I am suppose to do, but as I understood it wasn't hard.
\item \textbf{Q:} Any comments/suggestions for the course so far?

      \textbf{A:} 

\end{enumerate}
 

\end{document}